Untitled Draft

### 2023-03-15 doc/manuscript.Rmd

```{r load-targets, include=FALSE}
tar_load(data_clean)
tar_load(purdy_pictures)
tar_load(model_tables)
tar_load(demog_table)
tar_load(table_1)
pretty <- function(x) format(x, big.mark = ",")
```

>>>>

```{r load-targets, include=FALSE}
tar_load(model_list_by_age)
tar_load(data_clean)
tar_load(purdy_pictures)
tar_load(model_tables)
tar_load(demog_table)
tar_load(table_1)
pretty <- function(x) format(x, big.mark = ",")
```
